Fast and adaptive cointegration based model for forecasting high frequency financial time series

### 2017-01-17 articles-conferences/iscef2016/body.tex
comments 6,7,9

Cointegration relationship can be found in low and high frequency data of two or
more assets. While cointegration in low frequency data is motivated by a
long-run equilibrium relationship between economic forces, cointegration in high
frequency data has its foundation in statistical arbitrage which is very helpful
to detect mean-reverting trades. Cointegration at different data frequencies may
differ. \cite{rittler2012} shows how cointegration appears when the data
frequency is increased.

@@

The goal of our next experiment was to find a relation between this ratio $PC$
and the performance measure MSE (see equation \ref{eq:MSE}). $L$ was defined
between $[700,1500]$ data points with step size 100 and $p$ took values between
$[1,5]$ with step size 1.

@@

Figure~\ref{fig:cointvsmse} shows the relation between MSE and $PC$ and $L$.  We
found that better cointegration percentage leads to better performance accuracy
in terms of reducing MSE.

@@

\section{Experimental results}
\label{sec:results}
\subsection{Data} \label{sec:unitroot}
AVECM tests were carried out using four foreign exchange rates all related to
USD: EURUSD, GBPUSD, USDCHF and USDJPY. This data was collected from
\cite{Dukascopy2014}, a free database which gives access to the Swiss Foreign
Exchange marketplace.

>>>>

Cointegration relationship can be found in low and high frequency data of two or
more assets. While cointegration in low frequency data is motivated by a
long-run equilibrium relationship between economic forces, cointegration in high
frequency data has its foundation in statistical arbitrage which is very helpful
to detect mean-reverting trades. Information, about cointegrated assets in high
frequency data could be used as an input for high frequency trading strategies,
using it as signal to capture small profits in short term trades, see
\cite{miao2014}. \cite{zhou2001} addresses the benefits of using higher
frequency data to analize cointegration. \cite{rittler2012} also found that
cointegration may differ with different data frequencies and it could appear
when the data frequency is increased.

@@

The goal of our next experiment was to find a relation between this ratio $PC$
and the performance measure MSE (see equation \ref{eq:MSE}). $L$ was defined
between $[2,14]$ hours, that corresponds to $[720, 5040]$ data points, and $p$
took values between $[1,5]$.

@@

Figure~\ref{fig:cointvsmse} shows the relation between MSE and $PC$ and $L$.  We
found that better cointegration percentage leads to better performance accuracy
in terms of reducing MSE. Also, increasing the size of the sliding window $L$
doesn't necessarily help to reduce MSE.

@@

\section{Experimental results}
\label{sec:results}
\subsection{Data} \label{sec:unitroot}
All the experiments and AVECM tests were carried out using four foreign exchange rates all related to
USD: EURUSD, GBPUSD, USDCHF and USDJPY. We chose the most traded rates related
to USD so they are likely to be cointegrated. 
This data was collected from
\cite{Dukascopy2014}, a free database which gives access to the Swiss Foreign
Exchange marketplace.
